Quantum Interval-Valued Probability: Contextuality and the Born Rule

### 2017-08-15 prop_letter.tex
KS

The technical question is what happens if we relax the perfect
measurement assumption that the intervals are precisely $[0,0]$ and
$[1,1]$. We need to examine what happens if measurement imperfections
occasionally cause an ideally impossible event to be detected or an
ideally certain event not to be detected. Mermin argues in this case
that:
\begin{quote}
  \ldots although the outcomes deduced from such imperfect
  measurements will occasionally differ dramatically from those
  allowed in the ideal case, if the misalignment is very slight, the
  statistical distribution of outcomes will differ only slightly from
  the ideal case~\citep{Mermin1999}.
\end{quote}

@@

As $\delta$ gets bigger, the QIVPM allows more and more indeterminate
behavior. A $\frac{1}{3}$-deterministic QIVPM can be given by
$\bar{\mu}\left(P\right)=\left[x/3,x/3\right]$, where $P$ projects
onto an $x$-dimensional subspace of a three-dimensional Hilbert space.

We now prove that for small enough $\delta$, the Kochen-Specker result is
still valid, i.e., if the measurement imperfections are small enough,
we cannot nullify the Kochen-Specker theorem as
Meyer~\cite{PhysRevLett.83.3751} argued.

\begin{thm}[Kochen-Specker~\cite{kochenspecker1967,peres1995quantum,Redhead1987-REDINA}]\label{thm:Kochen-Specker}
  Given a Hilbert space $\Hilb$ of dimension~$d\ge3$, there is no
  0-deterministic
  measure~$\mu^{\mathrm{D}}:\events\rightarrow\left\{ 0,1\right\}
  $.\end{thm}

We will proceed by assuming a 0-deterministic QIVPM $\bar{\mu}$ and
derive a contradiction using the following nine ``Mermin-Peres
square''
observables~$\mathbf{O}_{ij}$~\cite{Mermin1990Simple,peres1995quantum}:
\begin{center}
\begin{tabular}{|c|c|c|}
\hline 
$\mathbb{1}\otimes\sigma_{z}$  & $\sigma_{z}\otimes\mathbb{1}$  & $\sigma_{z}\otimes\sigma_{z}$ \tabularnewline
\hline 
$\sigma_{x}\otimes\mathbb{1}$  & $\mathbb{1}\otimes\sigma_{x}$  & $\sigma_{x}\otimes\sigma_{x}$ \tabularnewline
\hline 
$\sigma_{x}\otimes\sigma_{z}$  & $\sigma_{z}\otimes\sigma_{x}$  & $\sigma_{y}\otimes\sigma_{y}$ \tabularnewline
\hline 
\end{tabular}\,,
\par\end{center}

@@

@@

@@

>>>>

KS is formulated under the assumption that all observables for a QM
system have definite values at all times. (cite)

Our QIVPM framework allows us to reformulate KS by relaxing this
assumption.

This quantifies Mermin's argument:

\begin{quote}
  \ldots although the outcomes deduced from such imperfect
  measurements will occasionally differ dramatically from those
  allowed in the ideal case, if the misalignment is very slight, the
  statistical distribution of outcomes will differ only slightly from
  the ideal case~\citep{Mermin1999}.
\end{quote}

%%%%%
\subsection{$\delta$-Determinism}

The technical question is what happens if we relax the perfect
measurement assumption that the intervals are precisely $[0,0]$ and
$[1,1]$. We need to examine what happens if measurement imperfections
occasionally cause an ideally impossible event to be detected or an
ideally certain event not to be detected.

@@

As $\delta$ gets bigger, the QIVPM allows more and more indeterminate
behavior. We now prove that for small enough $\delta$, the Kochen-Specker result is
still valid, i.e., if the measurement imperfections are small enough,
we cannot nullify the Kochen-Specker theorem as
Meyer~\cite{PhysRevLett.83.3751} argued.

%%%%%
\subsection{Expectation Values of Fuzzy Observables}

@@

%%%%%
\subsection{Finite Precision KS}

Statement of reformulated KS
\begin{thm}[Kochen-Specker~\cite{kochenspecker1967,peres1995quantum,Redhead1987-REDINA}]\label{thm:Kochen-Specker}
  Given a Hilbert space $\Hilb$ of dimension~$d\ge3$, there is no
  0-deterministic
  measure~$\mu^{\mathrm{D}}:\events\rightarrow\left\{ 0,1\right\}
  $.\end{thm}

Proof of reformulated KS. We will proceed by assuming a 0-deterministic QIVPM $\bar{\mu}$ and
derive a contradiction using the following nine ``Mermin-Peres
square''
observables~$\mathbf{O}_{ij}$~\cite{Mermin1990Simple,peres1995quantum}:
{\renewcommand{\arraystretch}{2}%
\begin{center}
\begin{tabular}{|@{\quad}c@{\quad}|@{\quad}c@{\quad}|@{\quad}c@{\quad}|}
\hline 
$\mathbb{1}\otimes\sigma_{z}$  & $\sigma_{z}\otimes\mathbb{1}$  & $\sigma_{z}\otimes\sigma_{z}$ \tabularnewline
\hline 
$\sigma_{x}\otimes\mathbb{1}$  & $\mathbb{1}\otimes\sigma_{x}$  & $\sigma_{x}\otimes\sigma_{x}$ \tabularnewline
\hline 
$\sigma_{x}\otimes\sigma_{z}$  & $\sigma_{z}\otimes\sigma_{x}$  & $\sigma_{y}\otimes\sigma_{y}$ \tabularnewline
\hline 
\end{tabular}\,,
\par\end{center}
}

@@

\paragraph*{Stronger KS: Main Result.}

@@

%%%%%
\subsection{HV}

A $\frac{1}{3}$-deterministic QIVPM can be given by
$\bar{\mu}\left(P\right)=\left[x/3,x/3\right]$, where $P$ projects
onto an $x$-dimensional subspace of a three-dimensional Hilbert space.
